Ideology and Identity; Machine Learning Application

### 2021-05-13 Paper Markdown.Rmd
final Rmd

srv_ideo <- read.csv("DataTurn/srv_ideo.csv")
srv_use <- read.csv("DataTurn/srv_use.csv")

# For reproduction from scratch using ANES data
#source("Scripts/load and first clean.R")
```
### Abstract

>>>>

srv_ideo <- read.csv("Data/DataTurn/srv_ideo.csv")
srv_use <- read.csv("Data/DataTurn/srv_use.csv")

# For reproduction from scratch using ANES data
#source("Scripts/load and first clean.R")
```

### Abstract
